\sysfull

### 2018-04-17 paper/implementation.tex
impl: remove redundant text

We implemented \sys's programming and execution model as a runtime library and API that a programmer can use to make a plain C program intermittence-safe using \sys.

@@

Coala's API adds only five syntactic constructs to a C-based language, summarized
in Table~\ref{table:coala_api}.
\texttt{COALA\_TASK} is a function annotation that declares a function to be a
task. \texttt{COALA\_NEXT\_TASK}, indicates the task to run next, after an
executing task completes.  \texttt{COALA\_PV} declare a new protected variable.
The programmer uses \texttt{RP} and \texttt{WP}, to read and write protected
respectively.  \texttt{COALA\_SM} identifies protected \texttt{struct} fields
and tells \sys to ensure that the struct fields are page-aligned in memory.
The programmer is required to explicitly call two API functions at the start of
{\tt main()}: \texttt{COALA\_INIT}, which does global initialization upon first
boot and \texttt{COALA\_RUN} which hands the control to \sys's task manager to
resume task execution.

@@

\subsection{API Details}

>>>>

We implemented \sys's programming and execution model as a runtime library and API that a programmer can use to make a plain C program intermittence-safe.

@@

Coala's API adds only five syntactic constructs to a C-based language, summarized
in Table~\ref{table:coala_api}.

%\texttt{COALA\_TASK} is a function annotation that declares a function to be a
%task. \texttt{COALA\_NEXT\_TASK}, indicates the task to run next, after an
%executing task completes.  \texttt{COALA\_PV} declare a new protected variable.
%The programmer uses \texttt{RP} and \texttt{WP}, to read and write protected
%respectively.  \texttt{COALA\_SM} identifies protected \texttt{struct} fields
%and tells \sys to ensure that the struct fields are page-aligned in memory.
%The programmer is required to explicitly call two API functions at the start of
%{\tt main()}: \texttt{COALA\_INIT}, which does global initialization upon first
%boot and \texttt{COALA\_RUN} which hands the control to \sys's task manager to
%resume task execution.

@@

%\subsection{API Details}
